---
title: "Analysis pipeline of applying XConTest to Yao 2023"
author: "Tianyu Zhang, Ergan Shang and Kathryn Roeder"
format: html
editor: visual
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
rm(list = ls())
library(ggpubr)
library(grid)
library(ggnewscale)
library(readxl)
library(here)
library(glue)
library(data.table)
library(ggplot2)
library(igraph)
library(doParallel)
library(foreach)
library(highmean)
library(scales)
library(dplyr)
library(Seurat)
library(patchwork)
library(reshape2)
library(tidyverse)
library(grpreg)
library(HMC)

#these are for gene clustering in 31_ and D1_
library(CSCORE)
library(WGCNA)
library(dynamicTreeCut)
library(clusterProfiler)
library(org.Hs.eg.db)
library(parallel)
library(corrplot)

work_directory <- here::here()
code_directory <- paste0(work_directory, '/yao_2023/code')
code_directory |> print()
```

## Data preprocessing

The original data can be downloaded from [GEO](https://www-ncbi-nlm-nih-gov.proxy.library.ucsb.edu/geo/query/acc.cgi?acc=GSM6858447).

```{r, eval = FALSE}
source(file.path(code_directory, '01_subsetting_genes.R'),
       local = TRUE)
source(file.path(code_directory, '02_remove_cell_cycle.R'),
       local = TRUE)
source(file.path(code_directory, '03_structure_residuals.R'),
       local = TRUE)
source(file.path(code_directory, '04_subsetting_perturbation.R'),
       local = TRUE)
```

## Establishing the gene modules using `CSCORE`

```{r, eval = FALSE}
source(file.path(code_directory, '31_establish_clustering.R'),
       local = TRUE)
```

### Perform GO analysis to each gene module

```{r, eval = FALSE}
source(file.path(code_directory, '32_GO_analysis.R'),
       local = TRUE)
```

### Create the representative GO term table for selected modules

```{r}
source(file.path(code_directory, '33_GO_table.R'),
       local = TRUE)
```

## Results of XConTest

### Apply aggregated XConTest to all perturbations. Probably want to run this on a cluster.

```{r, eval = FALSE}
system2("Rscript", file.path(code_directory, "51_systematic_process_all_in_paper_cluster.R"))
system2("Rscript", file.path(code_directory, "52_process_results_cluster.R"))
```

### Create igraph for each module.

```{r, eval = FALSE}
source(file.path(code_directory, '54_graph_visualization.R'),
       local = TRUE)
```

### Create the convergence plot for XConTest

```{r}
source(file.path(code_directory, '91_overall_convergence_and_number_module.R'),
       local = TRUE)
```

### Create the directional convergence plots for XConTest

```{r}
source(file.path(code_directory, '92_directional_convergence_and_count_matrix.R'),
       local = TRUE)
```

### Create the scLinker Plot by XConTest

```{r}
source(file.path(code_directory, 'C1_scLinker_XConTest.R'),
       local = TRUE)
```

## Results of Dset

### Apply Dset to all perturbations and all modules. Probably want to run this on a cluster.

```{r, eval = FALSE}
system2("Rscript", file.path(code_directory, "A1_chen_method.R"))
system2("Rscript", file.path(code_directory, "A2_process_result.R"))
```

### Create the convergence plot for Dset

```{r}
source(file.path(code_directory, 'A3_chen_convergence_and_number_module.R'),
       local = TRUE)
```

## Perturbation pairs of more interest

```{r}
source(file.path(work_directory, 'R/collect_and_structure_results.R'))
```

### Examine perturbation pairs with more convergent modules

```{r}
source(file.path(code_directory, 'B1_collect_many_module_converge.R'),
       local = TRUE)
```

### Create igraph for perturbations with $\geq 3$ convergent modules.

```{r}
source(file.path(code_directory, 'B2_create_perturbation_igraph.R'),
       local = TRUE)
```

### Examine selected perturbation pairs

```{r}
source(file.path(code_directory, 'B3_venn_diagram.R'),
       local = TRUE)
```

### Create the scLinker Plot by Dset

```{r, eval = FALSE}
source(file.path(code_directory, 'C2_scLinker_Dset.R'),
       local = TRUE)
```

### Create the LOEUF Plot

```{r, eval = FALSE}
source(file.path(code_directory, 'C3_hist_LOEUF.R'),
       local = TRUE)
```

## Change the gene modules for sensitivity analysis

As a sensitivity analysis, we restricted the feature set to genes from the
immunity-relevant modules and reran XConTest using lasso rather than group
lasso as the classifier. In this analysis, selected features are individual
genes rather than gene modules.

```{r, eval = FALSE}

work_directory_yao_2023 <- file.path(work_directory, "yao_2023")
source(file.path(code_directory, 'F1_truncate_gene_list.R'),
        local = TRUE) #only keep immunity modules
source(file.path(code_directory, 'G1_systematic_process_all_in_paper_cluster.R'),
        local = TRUE) # use lasso as the classifier
source(file.path(code_directory, 'G2_process_results_cluster.R'),
        local = TRUE) # process lasso results at the gene level
source(file.path(code_directory, 'G3_overall_convergence_and_number_module.R'),
        local = TRUE) # plot convergence and overlapping selected genes
```
